---
title: "Expert advice from experts"
author:
- familyname: Curie
  othernames: Marie
  address: University of Paris
  qualifications: Nobel Prize, PhD
- familyname: Curie
  othernames: Pierre
  address: University of Paris
  qualifications: Nobel Prize, PhD
email: mcurie.notreal@gmail.com
phone: (03) 9905 2478
department: Department of\newline Econometrics &\newline Business Statistics
organization: Acme Corporation
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  monash::report:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE, messages=FALSE, warning=FALSE)
library(ggplot2)
library(tidyverse)
<<<<<<< HEAD
<<<<<<< HEAD
=======
library(lubridate)
>>>>>>> 6342d924a40092967b92282d3e620460caf13d9e
```



<<<<<<< HEAD
```{r read_data, fig.cap="Nice histogram", message=FALSE, warning=FALSE}
covid <- read_csv(file = "data/worldwidecases.csv")
=======
# Section 1
```{r, warning=FALSE}
# Get data US & Germany
covid <- read_csv(here::here("data/worldwidecases.csv")) 
>>>>>>> 6342d924a40092967b92282d3e620460caf13d9e
=======
```

```{r data, message=FALSE}
covid<-read_csv(file=here::here("data/worldwidecases.csv"))
>>>>>>> tutorial-KN
```
```{r covid-s1}
covidrate_vis_s1 <- covid %>%
  mutate(date= as.Date(dateRep, format = "%d/%m/%y"),
         cases_rates = ((1000*cases/popData2018) + 0.01),
         dead_rates = ((1000*deaths/popData2018) +0.01)) %>%
  dplyr::filter(date != "2020-12-31") %>%
#group_by(countriesAndTerritories, date) %>%
#summarize_at(vars(cases, deaths), cumsum) %>%
  dplyr::filter(countriesAndTerritories %in% c("United_States_of_America","Germany")) %>%
ggplot(aes(x = date, y = cases_rates) ) +
geom_line(color = "#1F9E8E") +
facet_wrap(~countriesAndTerritories) +
theme_bw() +
ggtitle("Covid cases (rates)")

<<<<<<< HEAD
<<<<<<< HEAD
# Section 3

```{r France-Sweden, echo= FALSE, fig.align = "center", fig.width = 6, fig.cap= "Rates of covid cases over time for selected countries" }
covidrate_vis <- covid %>%
 mutate(date= as.Date(dateRep, format = "%d/%m/%y"),
        cases_rates = ((1000*cases/popData2018) + 0.01),
        dead_rates = ((1000*deaths/popData2018) +0.01)) %>%
 dplyr::filter(date != "2020-12-31") %>%
  group_by(countriesAndTerritories, date) %>% 
  summarize_at(vars(cases, deaths), cumsum) %>% 
  dplyr::filter(countriesAndTerritories %in% c(
 "Sweden",
 "France")) %>%
 ggplot(aes(x = date, y = cases) ) +
 geom_line(color = "#1F9E8E")  +
 facet_wrap(~countriesAndTerritories) +
 theme_bw() +
 ggtitle("Covid cases (rates)")
covidrate_vis
```
In figure \@ref(fig:France-Sweden) we observe corona virus cases in France and Sweden. 
=======
# Section 2

```{r a, fig.cap="Rates of covid cases over time"}
covidrate_vis <- covid %>% 
mutate(date=as.Date(dateRep,format="%d/%m/%y"), cases_rates=((1000*cases/popData2018)+0.01), dead_rates=((1000*deaths/popData2018)+0.01))%>% dplyr::filter(date != "2020-12-31") %>% 
  dplyr::filter(countriesAndTerritories %in% 
                  c("Italy", 
                    "Germany")) %>% 
  ggplot(aes(x = date,y = cases_rates) ) + 
  geom_line(color = "#1F9E8E") + facet_wrap(~countriesAndTerritories) + 
  theme_bw() + 
  ggtitle("Covidcases (rates)") 

covidrate_vis
```
In figure, \@ref(fig:a) we observe the COVID-19 rates for Italy and Germany.


>>>>>>> tutorial-KN

=======
covidrate_vis_s1
```
In figure \@ref(fig:covid-s1) we observe the corona virus rates of Germany and US.
 
>>>>>>> 6342d924a40092967b92282d3e620460caf13d9e
